An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-10 draft.tex
Update abstract
This is a shorter version

\begin{abstract}
    Multi-population based optimization methods are parallel and asynchronous by
    nature; researchers take advantage of this to scale algorithms with
    distributed, multi-threaded, and parallel implementations. However, the design of
    parallel and distributed versions of multi-population algorithms for their
    execution in cloud infrastructures is not a trivial task. Designers need to
    adapt the algorithms to leverage the benefits of scalability, elasticity,
    fault-tolerance, reproducibility, and cost-effectiveness of reactive
    cloud-based systems. In this work, we present the design and
    implementation of a reactive container-based application for the execution
    of multi-population algorithms. The application can be used to execute
    multiple experiments, both locally or in a cloud environment. Researchers
    can deploy experiments by specifying the infrastructure as part of an
    experiment definition so that it is much easier to reproduce results. The
    performance of the platform and the benefits of a multi-population approach
    has been evaluated using an ensemble of Genetic  Algorithms (GAs) and
    Particle Swarm Optimization (PSO). Experiments show that the framework
    allows the combined algorithms to outperform, with a high probability,
    single-algorithm versions. The framework we provide also has fewer
    parameters to tune since single-algorithm parameters are selected randomly.
    The architecture and the implemented platform is an excellent alternative
    for locally or a cloud-based deployment.
\end{abstract}

>>>>

\begin{abstract} 
Multi-population based methods have been used extensively in
recent years to improve the performance of nature-inspired optimization
algorithms, these methods are parallel and asynchronous by nature; researchers
take advantage of this to scale algorithms with distributed, multi-threaded,
parallel and cloud-based implementations. However, the design of distributed
versions of multi-population algorithms for their execution in cloud
infrastructures is not a trivial task. Designers need to adapt the algorithms to
leverage the benefits of scalability, elasticity, fault-tolerance,
reproducibility, and cost-effectiveness of reactive cloud-based systems. In this
work, we present the design and implementation of a reactive container-based
application for the execution of multi-population algorithms. Researchers can
use the application to execute multiple experiments, both locally or in a cloud
environment and deploy experiments by specifying the infrastructure as part of
an experiment definition so that it is much easier to reproduce results. We
evaluated the performance of the platform and the benefits of a multi-population
approach by using an ensemble of Genetic Algorithms (GAs) and Particle Swarm
Optimization (PSO) in a benchmark for the optimization of continuous functions.
Experiments show that the framework allows the ensemble to outperform
single-algorithm versions. The framework we provide also has fewer parameters to
tune since subpopulation parameters are selected randomly. The architecture and
the implemented platform is an excellent alternative for locally or a
cloud-based deployment. 
\end{abstract}
